---
title: "Pixar Films Analysis"
subtitle: "Proposal"
author: 
  - name: "Yoseph Alramahi"
    affiliations:
      - name: "School of Information, University of Arizona"
description: "Project description"
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
editor: visual
code-annotations: hover
execute:
  warning: false
---

```{r}
#| label: load-pkgs
#| message: false
library(tidyverse)

library(pixarfilms)
pixar_films <- pixarfilms::pixar_films
public_response <- pixarfilms::public_response
```

## Dataset

```{r}
nrow(pixar_films)
ncol(pixar_films)
```

A brief description of your dataset including its provenance, dimensions, etc. as well as the reason why you chose this dataset.

Make sure to load the data and use inline code for some of this information.

The Pixar Films data set from Tidy Tuesday 2025 contains information about Pixar movies, including genres, run times, budgets, box office revenue, and ratings. The data set contains r nrow(pixar_films) movies and r ncol(pixar_films) variables. I chose this data set because I enjoy Pixar movies and the data is well suited for creating visualizations and exploring trends.

# Questions

How do Pixar movie ratings vary across genres and release years?

How do budget and run time relate to box office revenue across different pixar genres ?

# Analysis plan

-  i will analyze how movie ratings very across genres and release years. The variables used will include genre, release year, IMDb rating, and rotten tomatoes score. I plan to create visualizations that compare ratings across genres and examine trends over time.
- i will examine how budget and run time are related to box office revenue across different pixar movies genres i will use scatter plots to look for patterns in the data.
